Guide to repository of supplementary resources

### 2023-02-01 index.Rmd
Update links in index.Rmd

[The repository on github.](https://github.com/UZH-PEG/diversity_envresp1)

[The respository on Zenodo with DOI 10.5281/zenodo.6334544.](https://doi.org/10.5281/zenodo.6334544)

>>>>

[The repository on github, current version 0.9.2.](https://github.com/UZH-PEG/diversity_envresp1/releases/tag/v0.9.2)

[The respository on Zenodo with the versioned DOI 10.5281/zenodo.7594024
](https://zenodo.org/record/7594024#.Y9pZaC8w0Q8)
